fishtraits

### 2019-09-03 data-raw/web_scrape.Rmd
loop across FID's and genus's

Choose FID and Genus
```{r}
#select and search the FID dropdown
fid <- rd$findElement(using = 'css selector', "#fid-combo")
fid$clearElement()
#pass to search box
fid$sendKeysToElement(list(fid_text[1]))
#click matching one
clickObject("#ui-id-1")

@@

#select and search the Genus dropdown
genus <- rd$findElement(using = 'css selector', "#genus-combo")
genus$clearElement()
genus$sendKeysToElement(list(genus_text[1]))
#click matching one
clickObject('#ui-id-2')
```

Pick the columns we want
```{r}
#make sure the appropriate column boxes are checked
columns <- rd$findElement(using = 'css selector', '#ui-accordion-ac1-header-1')
columns$clickElement()

#selectors for all boxes that need to be checked
```

Submit search and download
```{r}
#select search box
clickObject("#searchSubmit")
#and download
clickObject("#downloadbtn")
```

>>>>

Choose FID and Genus
```{r}

for (i in 1:length(fid_text)) {
  #select and search the FID dropdown
  fid <- rd$findElement(using = 'css selector', "#fid-combo")
  fid$clearElement()
  #pass to search box
  fid$sendKeysToElement(list(fid_text[i]))
  #click matching one
  clickObject("#ui-id-1")

@@

  for (j in 1:length(genus_text)) {
    #select and search the Genus dropdown
    genus <- rd$findElement(using = 'css selector', "#genus-combo")
    genus$clearElement()
    genus$sendKeysToElement(list(genus_text[j]))
    #click matching one
    clickObject('#ui-id-2')

    #make sure the appropriate column boxes are checked
    columns <- rd$findElement(using = 'css selector', '#ui-accordion-ac1-header-1')
    columns$clickElement()

    #selectors for all boxes that need to be checked

    #select search box
    clickObject("#searchSubmit")
    #and download
    clickObject("#downloadbtn")
  }
}
```

Pick the columns we want
```{r}

```

Submit search and download
```{r}

```
